\textcolor{violet}{Reverse Correlation Uncovers More Complete Tinnitus Spectra \vspace{0.25cm}}

### 2023-03-27 paper/short/main_wc995.tex
201 response to reviewers (#205)
* Add a few words about bigger studies to come

* Update paper

* Edits from reviews

* Update paper

* Update paper
Edits from Adam

\section{Introduction}
% INTRO PARAGRAPH 1/3
\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound
in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S. \cite{bhattPrevalenceSeverityExposures2016},
a third of whom experience functional cognitive impairment and diminished quality of life
\cite{nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
Clinical guidelines for tinnitus management involve targeted exposure to tinnitus-like sounds
in a habituation therapy termed \textit{sound therapy},
or as part of cognitive behavioral therapy \cite{tunkelClinicalPracticeGuideline2014}.
Critically, sound therapy outcomes improve when closely informed by the patient's internal tinnitus experience \cite{okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,schoisswohlAmplitudeModulatedNoise2019}.
However, existing strategies for characterizing tinnitus sounds, such as \textit{pitch matching} (PM),
are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent about 50-80\% of patients \cite{neffComparingThreeEstablished2019,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}.
There is a need for methods to characterize the remaining 20-50\% of nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.

% INTRO PARAGRAPH 2/3
Nontonal tinnitus sounds are presumed to be complex and heterogeneous
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021},
although few characteristics have been firmly established.
Therefore, we base our approach on \textit{reverse correlation} (RC),
an established behavioral method
\cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013}
for estimating internal perceptual representations that is unconstrained by prior knowledge about the representations themselves.
RC asks participants to render subjective judgments over random stimuli,
and reconstructs the latent signal as a linear combination of stimuli.
RC is closely related to Wiener theory,
which has inspired ``white-noise'' approaches to system characterization in physiology
\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering \cite{ljungSystemIdentificationTheory1998}.

@@

% document is a Latex  template for Technology Letters to be submitted to IEEE OJEMB \cite{ahumadaStimulusFeaturesSignal1971}. Submissions must have the sections listed in the following exactly in the order shown here: Introduction, Materials and Methods, Results, Discussion, Conclusions. Manuscripts to be submitted to IEEE OJEMB as a Science Letters must use a different template. For both types of manuscript, the authors can opt to add a Supplementary Materials section.

@@

\section{Materials and Methods}
% To use this template, type over sections of the template or cut and paste from another document. Highlight a section that you want to designate with a certain style, then select the appropriate name on the style menu. The style will adjust your fonts and line spacing. Do not change the font sizes or line spacing to squeeze more text into a limited number of pages. Use italics for emphasis; do not underline. 
% IEEE will do the final formatting of your paper. However, you should format your manuscript for submission to IEEE OJEMB for review and also for preparing for preprint that will be e-published several days after you upload the final version of an accepted manuscript.

@@

Our results show that RC can accurately reconstruct the frequency spectrum of certain relevant non-tonal tinnitus sounds.
Reconstruction accuracies observed here are below the simulated ideal, which may be attributed to noisy responses universally observed in applications of RC, and which may be mitigated by further optimizing the experimental protocol, stimulus generation, and reconstruction method.
For example, recent approaches to improving RC reconstruction methods can boost efficiency, noise robustness and overall accuracy \cite{comptonStimulusWhiteningImproves2022a}.
Subjects completed the required number of trials within 10 minutes,
indicating that this procedure can be conducted in a single clinical visit.
RC may therefore be useful as the basis for a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
Future work will focus on validating this approach with larger sample sizes, with more target signals,
stricter sound pressure level (SPL) control.

>>>>

\section{Introduction}
% INTRO PARAGRAPH 1/3
\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S.
\cite{bhattPrevalenceSeverityExposures2016}, a third of whom experience functional cognitive impairment and diminished quality of life \cite{nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
Clinical guidelines for tinnitus management involve targeted exposure to external sounds as part of \textit{sound therapy} or \textit{cognitive behavioral therapy} \cite{tunkelClinicalPracticeGuideline2014}.
Critically, patient outcomes improve when the employed external sounds are closely informed by the patient's internal tinnitus experience \cite{okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,schoisswohlAmplitudeModulatedNoise2019}.
However, existing strategies for characterizing tinnitus sounds, such as \textit{pitch matching} (PM), are best suited for patients whose tinnitus resembles pure tones (\eg ringing) \cite{neffComparingThreeEstablished2019,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}.
There is a need for methods to characterize tinnitus sounds in the estimated 20-50\% of patients with nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.

% INTRO PARAGRAPH 2/3
Nontonal tinnitus sounds are presumed to be complex and heterogeneous \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}, although few characteristics have been firmly established.
Therefore, we base our approach on \textit{reverse correlation} (RC), an established behavioral method \cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013} for estimating internal perceptual representations that is unconstrained by prior knowledge about the representations themselves.
RC asks participants to render subjective judgments over ambiguous stimuli, and reconstructs the latent representation by regressing subject responses onto the stimuli.
RC is closely related to Wiener theory, which has inspired ``white-noise'' approaches to system characterization in physiology \cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering \cite{ljungSystemIdentificationTheory1998}.

@@

% document is a Latex  template for Technology Letters to be submitted to IEEE OJEMB \cite{ahumadaStimulusFeaturesSignal1971}.
% Submissions must have the sections listed in the following exactly in the order shown here: Introduction, Materials and Methods, Results, Discussion, Conclusions.
% Manuscripts to be submitted to IEEE OJEMB as a Science Letters must use a different template.
% For both types of manuscript, the authors can opt to add a Supplementary Materials section.

@@

\section{Materials and Methods}
% To use this template, type over sections of the template or cut and paste from another document.
% Highlight a section that you want to designate with a certain style, then select the appropriate name on the style menu.
% The style will adjust your fonts and line spacing.
% Do not change the font sizes or line spacing to squeeze more text into a limited number of pages.
% Use italics for emphasis; do not underline.

% % IEEE will do the final formatting of your paper.
% However, you should format your manuscript for submission to IEEE OJEMB for review and also for preparing for preprint that will be e-published several days after you upload the final version of an accepted manuscript.

@@

Our results show that RC can accurately reconstruct the frequency spectrum of tinnitus-like sounds relevant to non-tonal tinnitus,
and therefore represent a proof of concept for using RC to characterize non-tonal tinnitus.
Subjects completed the required number of trials within ten minutes,
indicating that this procedure could be conducted within a single clinical visit.
RC may therefore be useful as the basis for a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
Reconstruction accuracies observed here are below the simulated ideal, which may be attributed to noisy responses universally observed in applications of RC,
and which may be mitigated by further optimizing the experimental protocol, stimulus generation, and reconstruction method.
For example, recent approaches to improving RC reconstruction methods can boost efficiency, noise robustness and overall accuracy \cite{comptonStimulusWhiteningImproves2022a}.
Future work will focus on more comprehensive validation of this approach, using larger sample sizes, more target sounds, and stricter control of sound presentation level.
